%%==================================================
%% abstract.tex for SJTU Master Thesis
%% based on CASthesis
%% modified by wei.jianwen@gmail.com
%% version: 0.3a
%% Encoding: UTF-8
%% last update: Dec 5th, 2010
%%==================================================


\begin{bigabstract}
  Shanghai Jiao Tong University (SJTU), directly subordinate to the Ministry of Education, is a key university in China, jointly run by the Ministry and Shanghai Municipality.

  SJTU has beautiful campuses, occupying an area of more than 200 hectare in total, and possesses plenty of advanced teaching and research equipment and facilities. Now, it has six campuses, the Xuhui, the Minhang, the Qibao, the Shangzhong Road , the Fahuazheng Road and the Chongqing Road(south). Over the past decade, the number of students in SJTU has grown from 5,000 to more than 38,000, the floorage of various buildings from 230,000 square meters to 800,000 square meters, and the area of campuses from 40ha to 200ha. Apart from the major buildings such as the Lecture Buildings, Laboratory Buildings, Dormitories and Gymnasiums, SJTU also has the Bao Zhaolong Library which is well-known throughout the country. Various laboratories, including university central laboratories such as "Computer Center" and "Audio-visual Education Center" are equipped with advanced research and teaching equipment and facilities.

An imperial edict issued in 1896 by Emperor Guangxu, established Nanyang Public School in Shanghai. The normal school, school of foreign studies, middle school and a high school were established. Sheng Xuanhuai, the person responsible for proposing the idea to the emperor, became the first president and is regarded as the founder of the university.

During the 1930s, the university gained a reputation of nurturing top engineers. After the foundation of People's Republic, some faculties were transferred to other universities. A significant amount of its faculty were sent in 1956, by the national government, to Xi'an to help build up Xi'an Jiao Tong University in western China. Afterwards, the school was officially renamed Shanghai Jiao Tong University.

Since the reform and opening up policy in China, SJTU has taken the lead in management reform of institutions for higher education, regaining its vigor and vitality with an unprecedented momentum of growth. SJTU includes five beautiful campuses, Xuhui, Minhang, Luwan Qibao, and Fahua, taking up an area of about 3,225,833 m2. A number of disciplines have been advancing towards the top echelon internationally, and a batch of burgeoning branches of learning have taken an important position domestically.

Today SJTU has 31 schools (departments), 63 undergraduate programs, 250 masters-degree programs, 203 Ph.D. programs, 28 post-doctorate programs, and 11 state key laboratories and national engineering research centers.

SJTU boasts a large number of famous scientists and professors, including 33 academics of the Academy of Sciences and Academy of Engineering, 92 accredited professors and chair professors of the "Cheung Kong Scholars Program" and more than 1,900 professors and associate professors.

Its total enrollment of students amounts to 42,881, of which 1,598 are international students. There are 17,766 undergraduates, and 24,017 masters and Ph.D. candidates. After more than a century of operation, Jiao Tong University has inherited the old tradition of "high starting points, solid foundation, strict requirements and extensive practice." Students from SJTU have won top prizes in various competitions, including ACM International Collegiate Programming Contest, International Mathematical Contest in Modeling and Electronics Design Contests. Famous alumni include Jiang Zemin, Lu Dingyi, Ding Guangen, Wang Daohan, Qian Xuesen, Wu Wenjun, Zou Taofen, Mao Yisheng, Cai Er, Huang Yanpei, Shao Lizi, Wang An and many more. More than 200 of the academics of the Chinese Academy of Sciences and Chinese Academy of Engineering are alumni of Jiao Tong University.

Welcome to Shanghai Jiao Tong University!

Established in 1896 as Nan Yang College, Shanghai Jiao Tong University is one of the first national institutions of higher learning in China. The name "Jiao Tong" comes from the book Yi Jing. Literally, "Jiao" means unite and "Tong" means harmony. In the book it says, when heaven and earth unite in deep harmony, peace and blessing descend upon all living things; when leaders and people unite and combine their influences, the nation enjoys universal flowering and prosperity.

With a shining history of more than 114 years, SJTU has grown with and shared weal and woe with the country. At present, it is implementing a grand blueprint for future development and determined to make continued efforts to build itself into a first class university in the world.

SJTU, as it is fondly called, is a dynamic and comprehensive university for excellent students education, cutting-edge scientific research and social service. From the early stage of its development, SJTU took first-class talents education as its principal mission. And today, it has been developed to the talent education idea of knowledge exploration, capacity development and personality nurturing.

Whether one is Academician or newly enrolled freshman, whether one’s field is mechanical engineering or contemporary literature, in the name of truth-seeking spirit, SJTU encourages its faculty and students to join a common search for answers to the fundamental and to the pressing questions that society is faced with. Members of the SJTU community are united by this spirit to pursue intellectual excellence, and dedicated to the discovery of knowledge in the classroom, the laboratory, and the community. For its members, SJTU has become the place where their dreams start to fly.

Besides its remarkable history, SJTU is also a university famous for its honored traditions. Its tradition of gratitude and responsibilities has already been deeply rooted in the hearts of its alumni, and to some, it has become their behavior philosophy.

As the 39th president of SJTU, I am not only proud of its glorious history, time-honored traditions and great contributions, but also proud of being kindly called “Brother Jie”（ “Jie Ge” in Chinese）by the students at SJTU. I really enjoy the time sharing and exchanging ideas and thoughts with them.

Thanks for your interest in SJTU and you are always welcome to visit us on campus or through the website en.sjtu.edu.cn at any time.

The Shanghai Jiao Tong University (SJTU) Library, from its humble origin as a small reading room built in 1896 upon the establishment of the Nan Yang Public School, is now one of the most venerable university libraries in China today. The SJTU Library system has come a long way since the construction of the first university library building in 1919. Laters additions included the Pao Sui-Loong Library on the Xuhui campus (October 1985), the Pao Yue-Kong Library on the Minhang campus (October 1992), and the Main Library on the Minhang campus (September 2008). The School of Agriculture Library from the Qibao campus became a member of SJTU Library system in September 1999, as did the School of Medicine Library from the Luwan campus, in June 2005.

SJTU Library has been committed to fostering innovation, practice and academic excellence, since its founding over a century ago. Over the years, SJTU Library has made great progress and achievements. SJTU Library system, with a total area of 63,700m2, currently comprises a number of branches covering a wide range of fields on natural and social science and technology. Affiliated libraries and reading rooms are housed in different schools and departments. Equipped with rich resources and state of the art facilities, SJTU Library is now boasts an open and integrated service system that facilitates and promotes research initiatives in all areas.

Following its time-honored tradition of having the readers’ best interests at heart while providing top quality services, the SJTU Library pursues the service idea of “Accessible study resources with integrated information infrastructure; Extended reference services for departments and research groups; Better library services supported by new technologies and research programs.” This facilitates its integrated and personalized services and enhances information literacy education. The functionalities of the library include holding, information retrieval and document delivery. The SJTU Library system plays an active role of a knowledge exchange and dissemination network with a focus on facilitating academic research and carrying forward the university’s cultural heritage.

A member of IFLA, the SJTU Library is also the Southeast Regional Center of CALIS, the Secretariat of the Steering Committee for the Academic Libraries of Shanghai, the Administration Center of the Shanghai Education Network Library and a branch of the Shanghai Central Library. SJTU Library is also the center for science and technology updates accredited by both the Ministry of Education and the Shanghai Science and Technology Commission. As the first of its kind in China, SJTU Library runs a “Library, Information Science and Archive-management” masters degree program.

\end{bigabstract}
